\begin{thebibliography}{123}

\bibitem{AnderT12}
I.M. Anderson and C.G. Torre:
{\em New symbolic tools for differential geometry, gravitation,
and field theory},
J. Math. Phys. {\bf 53}, 013511 (2012);\\
\url{http://digitalcommons.usu.edu/dg/}

\bibitem{atlas2}
\url{http://digi-area.com/Maple/atlas/}

\bibitem{Bard15}
G.V. Bard {\it Sage for Undergraduates}, Americ. Math. Soc. (2015);
preprint freely downloadable from \url{http://www.gregorybard.com/}

\bibitem{BirkaGSC17}
T. Birkandan, C. Güzelgün, E. Şirin and M. Can Uslu:
{\em Symbolic and Numerical Analysis in General Relativity with Open Source Computer Algebra Systems},
arXiv:1703.09738 (2017).

\bibitem{BolotP13}
D.A. Bolotin and S.V. Poslavsky: \emph{Introduction to Redberry: the computer algebra system designed for tensor manipulation}, arXiv:1302.1219 (2013);\\
\url{http://redberry.cc/}

\bibitem{snappy}
M. Culler, N. M. Dunfield, M. Goerner, and J. R. Weeks: {\em SnapPy, a computer program for studying the geometry and topology of 3-manifolds};\\
\url{http://snappy.computop.org}

\bibitem{Fletc67}
J.G. Fletcher, R. Clemens, R. Matzner, K.S. Thorne and B.A. Zimmerman:
{\em Computer Programs for Calculating General-Relativistic Curvature Tensors},
Astrophys. J. {\bf 148}, L91 (1967).

\bibitem{grtensorIII}
\url{https://github.com/grtensor/grtensor}

\bibitem{JoyneS14}
D. Joyner and W. Stein: {\it Sage Tutorial}, CreateSpace (2014).

\bibitem{KorolKS13}
A.V. Korol'kova, D.S. Kulyabov and L.A. Sevast'yanov:
{\em Tensor computations in computer algebra systems},
Prog. Comput. Soft.
{\bf 39}, 135 (2013).

\bibitem{Lee97}
J. M. Lee : {\em Riemannian Manifolds: An Introduction to Curvature},
Springer, New-York (1997).

\bibitem{Lee13}
J. M. Lee : {\em Introduction to Smooth Manifolds}, 2nd edition,
Springer, New-York (2013).

\bibitem{MacCa02}
M.A.H. MacCallum: {\em Computer Algebra in General Relativity},
Int. J. Mod. Phys. A {\bf 17}, 2707 (2002).

\bibitem{Marti08}
J.-M. Martin-Garcia: {\em xPerm: fast index canonicalization for tensor computer algebra}, Comput. Phys. Commun. {\bf 179}, 597 (2008);\\
\url{http://www.xact.es}

\bibitem{Milno56}
J. W. Milnor : {\em On manifolds homeomorphic to the 7-sphere},
Ann. Math. {\bf 64}, 399 (1956).

\bibitem{ONeil83}
B. O'Neill : {\em Semi-Riemannian Geometry, with Applications to Relativity},
Academic Press, New York (1983).

\bibitem{Peete07}
K. Peeters: {\em Symbolic field theory with Cadabra},
Comput. Phys. Commun. {\bf 15}, 550 (2007);\\
\url{https://cadabra.science/}

\bibitem{ricci}
\url{http://www.math.washington.edu/~lee/Ricci/}

\bibitem{sagemanifolds}
\url{http://sagemanifolds.obspm.fr}

\bibitem{Skea94}
J.E.F. Skea: \emph{Applications of SHEEP} (1994), lecture notes available at
\url{http://www.computeralgebra.nl/systemsoverview/special/tensoranalysis/sheep/}

\bibitem{Steen51}
N. Steenrod: \emph{The Topology of Fibre Bundles}, Princeton Univ. Press (Princeton) (1951)

\bibitem{SteinJ05}
W. Stein and D. Joyner: {\em SAGE: System for Algebra and Geometry Experimentation},
Commun. Comput. Algebra, {\bf 39}, 61 (2005).

\bibitem{Taube87}
C. H. Taubes : {\em Gauge theory on asymptotically periodic 4-manifolds},
J. Differential Geom. {\bf 25}, 363 (1987).

\bibitem{Toth05}
V. Toth: {\em Tensor manipulation in GPL Maxima},
arXiv:cs/0503073 (2005).

\bibitem{Zimme13}
P. Zimmermann et al.: {\it Calcul math\'ematique avec Sage}, CreateSpace (2013);
freely downloadable from \url{http://sagebook.gforge.inria.fr/}

\bibitem{Zimme18}
P. Zimmermann et al.: {\it Mathematical Computation with SageMath},
in preparation; preliminary version available at
\url{https://members.loria.fr/PZimmermann/sagebook/english.html}

\end{thebibliography}
